---
title: "lab1"
author: "Yuchen 201830360498 - Xuewen 201830120252"
date: "2021/9/8"
output: 
    html_document:
      toc: true
      toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
&nbsp;

### Exercise1
#### 1-1 Indexing into a data structure
***
```{r}
# A samle vecor
v <- c(1,4,4,3,2,2,3)
v[c(2,3,4)]
v[2:4]
v[c(2,4,3)]
```
&nbsp;

***
```{r}
# Create a sample data frame
data <- read.table(header=T, text='
 subject sex size
       1   M    7
       2   F    6
       3   F    9
       4   M   11
 ')

# Get the element at row 1, column 3
data[1,3]
data[1,"size"]


# Get rows 1 and 2, and all columns
data[1:2, ]   
data[c(1,2), ]


# Get rows 1 and 2, and only column 2
data[1:2, 2]
data[c(1,2), 2]

# Get rows 1 and 2, and only the columns named "sex" and "size"
data[1:2, c("sex","size")]
data[c(1,2), c(2,3)]

```
&nbsp;

***
```{r}
v > 2

v[v>2]
v[ c(F,T,T,T,F,F,T)]


```
&nbsp;

***
```{r}
# A boolean vector   
data$subject < 3
    
data[data$subject < 3, ]
data[c(TRUE,TRUE,FALSE,FALSE), ]

# It is also possible to get the numeric indices of the TRUEs
which(data$subject < 3)

```
&nbsp;

***
```{r}
# Here's the vector again.
v

# Drop the first element
v[-1]

# Drop first three
v[-1:-3]

# Drop just the last element
v[-length(v)]
```
&nbsp;

#### 1-2 Getting a subset of a data structure
&nbsp;

***
```{r}
# A sample vector
v <- c(1,4,4,3,2,2,3)

subset(v, v<3)
v[v<3]


# Another vector
t <- c("small", "small", "large", "medium")

# Remove "small" entries
subset(t, t!="small")
t[t!="small"]

```
&nbsp;

***
```{r}
v[v<3] <- 9

#subset(v, v<3) <- 9

```
&nbsp;

***
```{r}
# A sample data frame
data <- read.table(header=T, text='
 subject sex size
       1   M    7
       2   F    6
       3   F    9
       4   M   11
 ')


subset(data, subject < 3)
data[data$subject < 3, ]


# Subset of particular rows and columns
subset(data, subject < 3, select = -subject)
subset(data, subject < 3, select = c(sex,size))
subset(data, subject < 3, select = sex:size)
data[data$subject < 3, c("sex","size")]


# Logical AND of two conditions
subset(data, subject < 3  &  sex=="M")
data[data$subject < 3  &  data$sex=="M", ]


# Logical OR of two conditions
subset(data, subject < 3  |  sex=="M")
data[data$subject < 3  |  data$sex=="M", ]


# Condition based on transformed data
subset(data, log2(size) > 3 )
data[log2(data$size) > 3, ]


# Subset if elements are in another vector
subset(data, subject %in% c(1,3))
data[data$subject %in% c(1,3), ]


```
&nbsp;

#### 1-3 Making a vector filled with values
***
```{r}
rep(1, 50)

rep(F, 20)


rep(1:5, 4)

rep(1:5, each=4)



# Use it on a factor
rep(factor(LETTERS[1:3]), 5)

```
&nbsp;

### Exercise2
```{r}
data(pressure)
pressure[4,2] #row:4 col:2
pressure[,2]
```
&nbsp;

### Exercise3
```{r}
data(pressure)
plot(x = pressure$temperature, y = pressure$pressure)

plot(x = pressure$temperature, y = pressure$pressure, type = "l")

plot(x = pressure$temperature, y = pressure$pressure, xlab = "T", ylab = "P", type = "l")
```
&nbsp;

<font size=5>**Temperature and pressure are positively correlated with each other**</font>

&nbsp;

```{r}
?plot
```

&nbsp;

### Exercise4
```{r}
#load data
data(pressure)
# unit change
pressure["pressure"] <- pressure["pressure"]*133.322
pressure["temperature"] <- pressure["temperature"]+273.15
# calculate volumn
pressure["volumn"] <- 8.314*pressure["temperature"]/pressure["pressure"]
pressure["volumn"]
```
&nbsp;

### Exercise5
```{r}
data("women")
women["height"]
dim(women)
names(women)
```
&nbsp;

### Exercise6
```{r}
data("women")
plot(y = (women$height)^2, x = women$weight, ylab = "Squared Height", xlab = "Weight")
#TODO: describe the overall pattern
corelation <- cor((women$height)^2,women$weight)
fit<-lm((women$height)^2~women$weight)
abline(fit)
```
&nbsp;

<font size=5>**From the analysis above, the overall pattern for this data is linear**</font>
&nbsp;

### Exercise7
```{r}
data(women)
#unit exchange: kg=lbs/2.2046 m=inch*0.0254
women["height"] <- women["height"]*0.0254
women["weight"] <- women["weight"]/2.2046

#calculate BMI
women["BMI"] <- women["weight"]/women["height"]^2

#search for the largest and judge health condition
#BMI Categories:
#Underweight = <18.5
#Normal weight = 18.5–24.9
#Overweight = 25–29.9
#Obesity = BMI of 30 or greater

max_BMI = max(women["BMI"])
index <- which(women["BMI"]==max_BMI)
sprintf('The index of the highest BMI is %d, whose BMI is %f',index, max_BMI)
if(max_BMI <= 18.5){
    print("She is Underweight!")
} else if (max_BMI>18.5&&max_BMI<24.9) {
    print("She is at Normal weight!")
} else if (max_BMI>25&&max_BMI<29.9) {
    print("She is Overweight!")
} else {
    print("She is Obesity!")
}
```