---
title: "lab9"
author: "Yuchen Song_201830360498 - Xuewen Wang_201830120252"
date: "2021/11/24"
output: 
    html_document:
      toc: true
---
***
## <font color=blue>The data</font>
```{r}
load(url("http://www.openintro.org/stat/data/mlb11.RData"))
```


### <font color=blue>Ex1</font>
Scatter plot.  
```{r}
plot(mlb11$at_bats,mlb11$runs)
cor(mlb11$runs, mlb11$at_bats)
```
  
Yes, it is kind of linear, but the correlation is not strong enough.  
These two variables are quantitative/numerical variables, which are positively correlated, but as said above, they are not strongly correlated. Also, we can spot some obvious outliers from the imaginary regression line.  

***
## <font color=blue>Sum of squared residuals</font>
### <font color=blue>Ex2</font>
```{r}
plot_ss(x = mlb11$at_bats, y = mlb11$runs, showSquares = TRUE)
```
***
## <font color=blue>The linear model</font>
### <font color=blue>Ex3</font>
```{r, echo=FALSE}
m1 <- lm(runs ~ at_bats, data = mlb11)
```
```{r}
m2 <- lm(runs ~ homeruns, data = mlb11)
summary(m2)
```

  
The equation of the regression line is: $\hat{y}=415.2389+1.8345*homeruns$  
The slope tells us that whenever homeruns increse by a unit, there should be a 1.8345 units increase in the run.  

***
## <font color=blue>Prediction and prediction errors</font>
### <font color=blue>Ex4</font>
```{r}
plot(mlb11$runs ~ mlb11$at_bats)
abline(m1)
```

He would predict the runs at $\hat{y}=-2789.2429+0.6305*5585=732.0996$.  
The true runs for at-bats of 5585 is 708, which indicates that this is an overestimation, by 732.0996-708=24.0996.
```{r}
subset(mlb11,mlb11$at_bats==5585)["runs"]
```

***
## <font color=blue>Model diagnosticss</font>
### <font color=blue>Ex5</font>
```{r}
plot(m1$residuals ~ mlb11$at_bats)
abline(h = 0, lty = 3)  # adds a horizontal dashed line at y = 0
```
  
The points are roughly evenly distributed around the dashed line, which implies that the model line is a good in Linearity, and that the two variables are linear correlated.  

***
### <font color=blue>Ex6</font>
```{r}
hist(m1$residuals)
qqnorm(m1$residuals)
qqline(m1$residuals)  # adds diagonal line to the normal prob plot
```
  
Based on the two plots, we can say that the nearly normal residuals condition appears to be met.  

***
### <font color=blue>Ex7</font>
Based on the residual plot, we can spot that the residuals are distributed evenly around the line, so the constant variablilty condition has been met. 

***
## <font color=blue>Additional Exercises</font>
### <font color=blue>Ex8</font>
```{r}
plot(mlb11$hits,mlb11$runs)
m3 <- lm(runs ~ hits, data = mlb11)
abline(m3)
```
  
At the first glance, the two variables are roughly linearly correlated with each other.  

***
### <font color=blue>Ex9</font>
```{r}
summary(m1)
summary(m3)
```
  
The $R^2$ for runs and hits is 0.6419, while the $R^2$ for runs and at_bats is 0.3729, so this relationship is stronger than that of the first model.   
Yes, in most of the time, the model with larger R_squared is a better fitting of the data, in other words, the prediction using this model is more accurate.  

***
### <font color=blue>Ex10</font>

```{r}
plot(mlb11$wins,mlb11$runs)
cor(mlb11$wins,mlb11$runs)
m4 <- lm(runs ~ wins, data = mlb11)
abline(m4)
summary(m4)
```

```{r}
plot(mlb11$bat_avg,mlb11$runs)
cor(mlb11$bat_avg,mlb11$runs)
m5 <- lm(runs ~ bat_avg, data = mlb11)
abline(m5)
summary(m5)
```
  
From what has been demonstrated above, we can say that the best variable to predict the runs is bat_avg, with R_Square of 0.6561 and cor of 0.8099859.  